Through the eyes of the teacher

### 2022-06-18 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
upload demo datat
noch mehr plottsssss

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

@@

# changing gender female 2 = 0 
demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Male" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

>>>>

# prepare data (selected from questionnaire data)
demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")

@@

# changing gender female 2 = 1 
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

@@

# #filter --> 121 two times
# demo.data <-  demo.data[-c(28), ]

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Female" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )
